Analysis Anomalous Doppler Effect from quantum theory to classical dynamic simulation

### 2025-05-08 paper modification/CPB-tex-template/CPB Template-LaTeX/paper.tex
new edition

%=================================================================================================%
% This is a template designed for Chin. Phys. B (Dated 12 November 2014)
% Only one step to compile: PDFTeXify
%=================================================================================================%
\documentclass{cpbtex}
\bibliographystyle{iopart-num} 
\begin{document}
\begin{CJK*}{GBK}{song}

\title{Manuscript title}

@@

\begin{abstract}
The abstract is a concise (short and clear) summary of your work. It should clearly state the problem, the methods used, the main results, and the conclusions, and should not include citations and formulas.
\end{abstract}

>>>>

%=================================================================================================%
% This is a template designed for Chin. Phys. B (Dated 12 November 2014)
% Only one step to compile: PDFTeXify
%=================================================================================================%
\documentclass{cpbtex}
\usepackage{graphicx}% Include figure files
\usepackage{dcolumn}% Align table columns on decimal point
\usepackage{bm}% bold math
%\usepackage[backend=biber]{biblatex}
%\usepackage[mathlines]{lineno}% Enable numbering of text and display math
%\linenumbers\relax % Commence numbering lines

\graphicspath{{Figure/}}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{etoolbox}
\usepackage{microtype} 
\usepackage{caption}
\usepackage{hyperref}
\captionsetup[figure]{labelfont=bf, name=Fig., labelsep=period}
\bibliographystyle{iopart-num} 
\graphicspath{{Figure/}}

\begin{document}
\begin{CJK*}{GBK}{song}

\title{Analysis Anomalous Doppler Effect from quantum theory to classical dynamic simulation}

@@

\begin{abstract}
A quantum model combined with angular momentum conservation is established to analyze the process of Normal Doppler Effect and Anomalous Doppler Effect, illustrating that the resonance process is related to the angular momentum of the wave. The angular momentum resonant condition is numerically tested, and the energy change ratio between parallel and gyrokinetic energies during electron-wave resonance is calculated, showing strong agreement with quantum theory.
\end{abstract}
